{Hierarchy Builder:}\\ {Algebraic hierarchies} \\ {made easy} {in {\sc Coq} with {\sc Elpi}}

### 2020-07-02 talk-fscd/main.tex
Fix: TPHOL*s*
small fix

\begin{frame}[fragile]
  \frametitle{Implementations in DTT (packed classes) \\ \hfill [TPHOL
    2009]}

@@

  \begin{itemize}
  \item {\sc Coq/Mathcomp}:     canonicals \alert<1>{$+$ boilerplate
      $+$ validator [IJCAR]}
  \item {\sc Coq/Math-Classes}: type classes \alert<1>{$+$ boilerplate $+$ hints}
  \item {\sc Lean3/Mathlib}:     type classes \alert<1>{$+$ priorities $+$ linter}
  \item {\sc Agda}:             records \alert<1>{$+$ open and renaming directives}
  \end{itemize}

>>>>

\begin{frame}[fragile]
  \frametitle{Implementations in DTT (packed classes) \\ \hfill [TPHOLs
    2009]}

@@

  \begin{itemize}
  \item {\sc Coq/Mathcomp}:     canonicals \alert<1>{\\
      $+$ heavy boilerplate $+$ validator [IJCAR K.S. paper]}
  \item {\sc Coq/Math-Classes}: type classes \alert<1>{$+$ boilerplate $+$ hints}
  \item {\sc Lean3/Mathlib}:     type classes \alert<1>{$+$ priorities $+$ linter}
  \item {\sc Agda}:             records \alert<1>{$+$ open and renaming directives}
  \end{itemize}
